Drake Plan

### 2019-08-21 R/drake_plan_conus.Rmd
[read_mcd10_one]

aer_files_path = "/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/ALL_POINTS/"
date_start = "2018-01-01" # do not include in sel_data_bytime if don't want to limit
date_end   = "2018-12-31" # do not include in sel_data_bytime if don't want to limit
geo_region = "NEMIA"
sats = c("terra", "aqua")
# MCD19 data: 
mcd19path = "/data-coco/mcd19/fst/nemia/2018/" # now there is only 2018 data 
mcd19path_CONUS = "/data-coco/mcd19/fst/conus/2018/"
# point to cache: 
ssd_cache = new_cache(path = "/scratch/cache/aeronet_drake")

# for reporting purpose
y_var = "diff_AOD"
y_var_pred = "diff_AOD_pred"

# CONUS Drake Plans  ------------------------------------------------------------
source(here("R/drake_funcs.R"))
nemia_plan <- drake_plan(
  # 1.  Aeroent ---------------------------------------------------------------------

@@

  # 3. WPred Join MCD19 -----------------------------------------------------------
  # mcd is the large MCD19 dataset, limit to `refsub`:nearby(300km) when readin to 
  # control total lines, unable to read in all data together, too many rows
  mcd = target(read_mcd19(sat, file_in(mcd19path_CONUS)), transform = map(sat = c("terra", "aqua"))),
  # join is the rolling-joined dataset with aeronet
  join = target(rolling_join(mcd_sat = mcd, aer_data_wPred = wPred),
                transform = cross(mcd, wPred, .id = mcd)),

  # select aer sites in mcd19. further limit the stations
  sel_aer = target(aer_in_mcd19(aer_nearest_2, mcd19 = join),
             transform = map(join)),
  # buffers 
  ref = target(ref_in_buffer(region_aer_m = sel_aer, refgrid),
             transform = map(sel_aer)),
  # sites
  p = target(get_site_list(region_aer_m = sel_aer), transform = map(sel_aer)),
  n = target(get_site_name(region_aer_m = sel_aer), transform = map(sel_aer)),

  # mapping 
  # this way doesn't work:
  # sub_grid = target(select_refgrid_subset(ref_list0 = ref, point0 = p, name0 = n),
  #              transform = map(ref, p, n))
  sub_grid = target(purrr_pmap(ref = ref, p = p, n = n),
               transform = map(ref, p, n, .id = FALSE)),
  # calculate new vars to obtain the dataset ready for modeling for terra and aqua, using join, mcd, sub_grid 
  new_var = target(aod_MODIS_newVars(aod_join_MODIS = join, 
                                 MODIS_all = mcd, refDT_sub = sub_grid),
               transform = map(join, mcd, sub_grid, .id = c(join))),

  # 5. CV -----------------------------------------------------------
  cv_results = target(run_cv(dt = new_var),transform = map(new_var)),

  # 6. Report -----------------------------------------------------------
  print1 = target(report_rmse(cv_results),
                  transform = map(cv_results,.id = FALSE)),
  plot1 = target(plot_rmse(cv_results),
                 transform = map(cv_results,.id = FALSE)),
  plotSHAP1 = target(plot_SHAP(cv_results),
                 transform = map(cv_results,.id = FALSE)),
  report = rmarkdown::render(
    knitr_in("AOD_CONUS_Report.Rmd"),
    output_file = file_out("AOD_CONUS_Report.html"))
)
nemia_plan
#drake_plan_source(nemia_plan)
nemia_config <- drake_config(nemia_plan, cache = ssd_cache) # show the dependency
# vis_drake_graph(nemia_config, from = names(nemia_config$layout))
vis_drake_graph(nemia_config, ncol_legend = 0)

@@

```{r, eval = F}
make(nemia_plan, cache = ssd_cache)

future::plan(future::multiprocess)
options(future.globals.maxSize= 100*1024^3) 
make(nemia_plan, cache = ssd_cache,
     parallelism = "future", jobs = 20, cache_log_file = TRUE)

# to see the updated graph, run config again
nemia_config <- drake_config(nemia_plan, cache = ssd_cache) # show the dependency
vis_drake_graph(nemia_config)

>>>>

aer_files_path = "/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/ALL_POINTS/"
date_start = "2018-01-01" # do not include in sel_data_bytime if don't want to limit
date_end   = "2018-12-31" # do not include in sel_data_bytime if don't want to limit
geo_region = "NEMIA"
sats = c("terra", "aqua")
# MCD19 data: 
mcd19path = "/data-coco/mcd19/fst/nemia/2018/" # now there is only 2018 data 
mcd19path_CONUS = "/data-coco/mcd19/fst/conus/2018/"
out_dir = "/data-coco/mcd19/fst/conus/2018_AOD_newVar/"
# point to cache: 
ssd_cache = new_cache(path = "/scratch/cache/aeronet_drake")

# for reporting purpose
y_var = "diff_AOD"
y_var_pred = "diff_AOD_pred"
# how many features to print in scatterplots
n_vars = 4
# how many MCD days (files) to work on:
MCD_files_i = c(1:30)
# CONUS Drake Plans  ------------------------------------------------------------
source(here("R/drake_funcs.R"))
conus_plan <- drake_plan(
  # 1.  Aeroent ---------------------------------------------------------------------

@@

  # 3. WPred Join MCD19 -----------------------------------------------------------
  # mcd is the large MCD19 dataset, limit to `refsub`:nearby(300km) when readin to 
  # control total lines, unable to read in all data together, too many rows
  mcd = target(read_mcd19_one(i, sat = sat, file_in(mcd19path_CONUS)), 
               transform = cross( i = !!MCD_files_i, 
                                  sat = c("terra", "aqua")),
               format = "fst"),
  # join is the rolling-joined dataset with aeronet
  join = target(rolling_join(mcd_sat = mcd, aer_data_wPred = wPred),
                transform = cross(mcd, wPred, .id = mcd)),

  # select aer sites in mcd19. further limit the stations
  sel_aer = target(aer_in_mcd19(aer_nearest_2, mcd19 = join),
             transform = map(join)),
  # buffers 
  ref = target(ref_in_buffer(sel_aer, refgrid),
             transform = map(sel_aer)),
  # sites
  p = target(get_site_list(sel_aer), transform = map(sel_aer)),
  n = target(get_site_name(sel_aer), transform = map(sel_aer)),

  # mapping 
  # this way doesn't work:
  # sub_grid = target(select_refgrid_subset(ref_list0 = ref, point0 = p, name0 = n),
  #              transform = map(ref, p, n))
  sub_grid = target(purrr_pmap(ref = ref, p = p, n = n),
               transform = map(ref, p, n, .id = FALSE)),
  # calculate new vars to obtain the dataset ready for modeling for terra and aqua, using join, mcd, sub_grid 
  new_var = target(aod_MODIS_newVars(aod_join_MODIS = join, 
                                 MODIS_all = mcd, refDT_sub = sub_grid),
               transform = map(join, mcd, sub_grid, .id = c(join))),
  # deliver two rowbinded dataset: for terra and aqua 
  # binded = target(rbindlist(new_var),
  #                 transform = combine(new_var, .by = c(i, sat))),
  # `.id_chr` let you save the file using target names:
  out = target(write.fst(new_var, path = file.path(file_out(out_dir), .id_chr)), transform = map(new_var))
)

# 
# conus_plan_cv <- drake_plan(
#   # 5. CV -----------------------------------------------------------
#   cv_results = target(run_cv(dt = new_var),transform = map(new_var)),
#   
#   # 6. Report -----------------------------------------------------------
#   print1 = target(report_rmse(cv_results),
#                   transform = map(cv_results,.id = FALSE)),
#   plot1 = target(plot_rmse(cv_results),
#                  transform = map(cv_results,.id = FALSE)),
#   # figures
#   plotAOD = target(plot_AOD(cv_results),
#                  transform = map(cv_results,.id = FALSE)),
#   plotscatter = target(plot_scatter(cv_results),
#                  transform = map(cv_results,.id = FALSE)),
#   
#   shap_long = target(get_SHAP_long(cv_results),
#                   transform = map(cv_results,.id = FALSE)),
#   plotSHAP1 = target(plot_SHAP(shap_long),
#                  transform = map(shap_long,.id = FALSE)),
#   plotSHAP2 = target(plot_SHAP_scatter(cv_results, shap_long),
#                  transform = map(cv_results, shap_long,.id = FALSE)),
#   report = rmarkdown::render(
#     knitr_in("AOD_CONUS_Report.Rmd"),
#     output_file = file_out("AOD_CONUS_Report.html"))
# )
conus_plan
nrow(conus_plan)
#drake_plan_source(conus_plan)
if(nrow(conus_plan)<100){
nemia_config <- drake_config(conus_plan, cache = ssd_cache) # show the dependency
# vis_drake_graph(nemia_config, from = names(nemia_config$layout))
vis_drake_graph(nemia_config, ncol_legend = 0)
}
```

```{r, eval = F}
# make(conus_plan, cache = ssd_cache)

time0 <- Sys.time()
future::plan(future::multiprocess)
options(future.globals.maxSize= 100*1024^3) 
make(conus_plan, cache = ssd_cache,
     parallelism = "future", jobs = 5)
Sys.time() - time0

# to see the updated graph, run config again
nemia_config <- drake_config(conus_plan, cache = ssd_cache) # show the dependency
vis_drake_graph(nemia_config)

@@
